---
title: "Best Model For MTcars"
author: "Raghava KV"
output:  word_document

section_number: TRUE
editor_options: 
chunk_output_type: console
---
```{r tidyverse}
# Load the package tidyverse, dplyr is part of tidyverse
library(tidyverse)
library(caret)
library(MVN)
```
```{r}
data=mtcars[,-c(8,9)]
head(data)
```
```{r}
mod1=lm(mpg ~ wt, data = mtcars)
summary(mod1)
plot(mod1)

```
*Inference*
*This model is the basic maodel which I tried which find the direct realtion between the weight and the mpg*
*The error is not normal from the qq plot as it is not striaght*
*Residuals vs Fitted plot model is not exaclty linear it can be made linear by adding non linear terms*
*Weight is given 3stars it will effect the model*
*pvalue is almost near to zero but adjusted r square can be increased*
*Conclusion : From weight should be considered too*
```{r}
mod2=lm(mpg~wt+hp,data=mtcars)
summary(mod2)
plot(mod2)
```
*Inference*
*Compared to mod1 it has deceresed adjusted rsquare and residual error pvalue too decrease furthur*
*Hp importantplays an important role but not as important as weight*

```{r}
mod2=lm(mpg~wt+hp+disp,data=mtcars)
summary(mod2)
plot(mod2)
```
*THere is no musch difference between the above model and the below one,if not the decreased addjuste r square *
*The normal qqplot is also not stright this model *
```{r}
mod3=lm(mpg~wt+hp+cyl,data=mtcars)
summary(mod3)
plot(mod3)
```
*THere is no musch difference between the above model and the below one,if not the decreased addjuste r square *
*The normal qqplot is also not stright this model *
*This plot is better than the previous one but cylenders will effect the mpg to a certain effect* 
```{r}
mod4=lm(mpg~wt+hp*cyl,data=mtcars)
summary(mod4)
plot(mod4)
```
*I tried multiplying the hp and cylender,the adjusted r square is encereasing and the residual standard error is decreasing*
```{r}
mod5=lm(mpg~wt*cyl+hp*qsec,data=mtcars)
summary(mod5)
plot(mod5)
```

*
Residual standard error: 2.105 on 25 degrees of freedom
 Adjusted R-squared:  0.878  p-value: 2.087e-11
*
#Number speak themself :-D
*This is is the best model I came up with, theresidual error is min and the p value is almost near to zero, adjusted r square is not*
#But the problem is qq plot is not normal
_Trying to apply boxcock on this model_
```{r}
shapiro.test(mod5$residuals)
```
#The values are  W = 0.97829, p-value = 0.7484
So no need to  apply boxcock



```{r}
head(mtcars)
```