---
title: "Two-Way ANOVA"
author: "Dr.Sampath"
date: "24/02/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Loading required library
#install.packages("palmerpenguins")
library(palmerpenguins)
library(tidyverse)
library(lattice)
library(car)
```

```{r}
glimpse(penguins)
```
There are 344 observations in 8 features. We will take three features from the given data namely, `species`,`flipper_length_mm` and `sex`.
```{r}
DATA <- penguins %>% 
  select(species,flipper_length_mm,sex)
DATA <- na.omit(DATA) # Removed 11 observations
head(DATA)
```
```{r}
summary(DATA)
```
Out of 333 observations, 165 for female and 168 for male.

Plot
===

```{r}
ggplot(DATA)+
  aes(species,flipper_length_mm,color=sex)+
  geom_jitter(na.rm = TRUE)+ #  geom_point(position = "jitter")
  theme(legend.position="right")+
  labs(title="Species vs Flipper Length")
```


Here, the factor is the `species` variable which contains 3 groups (Adelie, Chinstrap and Gentoo). In each group, had two gender species.

Testing Hypothesis
===


The null and alternative hypothesis of an ANOVA are:

- $H_0:$ The three species are equal in terms of flipper length

- $H_1:$ At least one mean is different.


```{r}
ggplot(DATA)+
  aes(species,flipper_length_mm,color=sex)+
  geom_boxplot(na.rm = TRUE)+ # color, shape 
  theme(legend.position="left")+
  labs(title="Species vs Flipper Length")
```


We can see that there are outliers in Adelie group and in each group female penguine flipper length is small than male penguine in the data.

```{r}
anova_two_way <- aov(flipper_length_mm ~ species+sex,data=DATA
               )
```

```{r}
summary(anova_two_way)
```



As p-values are near to zero for two factors, we reject the null hypothesis. Thus there is a significance difference between in the popuplation mean across the factors.

```{r}
par(mfrow=c(1,2)) # combine plots
plot(anova_two_way,3)
plot(anova_two_way,2)
```


The observations 27, 85, and 124 effecting on heteroscedasticity and normal QQ plot suggest that the residuals are normal. We can check heteroscedasticity and normality statistically using leveneTest and Shapiro-Wilk test respectively.

```{r}
shapiro.test(anova_two_way$residuals)
```


As p-value (0.2952) is larger than 0.001, we do not reject null hypothesis. Thus the residuals are normal statistically.

Testing Hypothesis for Levense Test:

- $H_0:$ Variances are equal
- $H_1:$ at least one varaince is different

```{r}
# Levene's test from car library
leveneTest(flipper_length_mm ~ species*sex, data=DATA)
```

As p-value (0.03652) is larger than level of significance, we do not reject null hypothesis.



```{r}
Tk <- TukeyHSD(anova_two_way)
Tk
```


```{r}
plot(Tk)
```

No one of the species groups pairwise have the same mean.

Exercise:
===
- Perform Two-Way ANOVA for `bill_length_mm` with two factors `species` and `gender`

Assignment-IV:
===



This assignment for 20 Marks

 **Answer the following for the dataset 'ToothGrowth' from CRAN**
 
- Perform Exploratory Data Analysis (must include scatter plots, box-plots) (5 Marks)
- Choose your qualitative and quantitative variables in given data and perform One-Way ANOVA (5 Marks)
- Choose your variables from the data to perform Two-Way ANOVA (5 Marks)
- Presentation (5 Marks)
  

```{r}
head(ToothGrowth)
```





